Oregon 2013 Medication for Asthma Inhalers

### 2017-07-11 r_scripts/analysis/oregon_medication.Rmd
distributed casecrossover

DLestimate$lag <- 0:lag_max
p <- ggplot(DLestimate, aes(x=lag, y=estimate, ymin=lower, ymax=upper))
p <- p + geom_ribbon(alpha=.5) + geom_line(size=2)
p <- p + geom_line(aes(x=lag), linetype=2, size=2)
p <- p + theme_bw()
# p

@@

### Lag

### 1. For Overall Plot

@@

### 2. For Age Category

### 3. For Sex Category

>>>>

DLestimate$lag <- 0:lag_max
p <- ggplot(DLestimate, aes(x=lag, y=estimate, ymin=lower, ymax=upper))
p <- p + geom_ribbon(alpha=.5) + geom_line(size=2)
p <- p + geom_line(aes(x=lag), linetype=2, size=2)
p <- p + theme_bw()
p

@@

### 1. For Overall Plot (Unconstrained lag model)

@@

### 2. Distributed lag for casecrossover

```{r DLM for casecrossover, echo = FALSE, message=FALSE, warning=FALSE}
read_path8 <- paste0("../data_new/county_data/zip_to_county_new.csv")
or_zip_to_county <- read_csv(read_path8)

which(colnames(inhaler_ndc_lag_df)=="geo_smk_pm10_zip") # 159
which(colnames(inhaler_ndc_lag_df)=="geo_smk_pm10_lag1_zip") # 160
which(colnames(inhaler_ndc_lag_df)=="wrf_temp_zip") # 93
which(colnames(inhaler_ndc_lag_df)=="wrf_temp_lag1_zip") # 150

inhaler_geo_lag <- inhaler_ndc_lag_df %>%
  select(159, 160:166) # GWR-method

inhaler_temp_lag <- inhaler_ndc_lag_df %>%
  select(93, 150:156) # GWR-method

lag_max <- 7
n1 <- length(inhaler_geo_lag[,1])
n2 <- length(inhaler_temp_lag[,1])

inhaler_geo_lag <- as.matrix(inhaler_geo_lag)
inhaler_temp_lag <- as.matrix(inhaler_temp_lag)

# the nrow B should equal ncol(pm)
dim(B)

inhaler_geo_lag_B <- inhaler_geo_lag%*%B
inhaler_temp_lag_B <- inhaler_temp_lag%*%B

fit <- clogit(outcome ~ inhaler_geo_lag_B + inhaler_temp_lag_B + strata(personkey), 
              inhaler_ndc_lag_df)

coef(fit)
summary(fit)
AIC(fit)

D <- cbind(B,B)

# dlparms <- grep("inhaler_geo_lag", names(coef(fit)))
dlparms <- c(1,2,3,4,5,6)
DLestimate<- data.frame(estimate=D%*%coef(fit)[dlparms]) 
DLvar <- D%*%vcov(fit)[dlparms,dlparms]%*%t(D)
DLestimate$SE <- sqrt(diag(DLvar))
DLestimate$lower <- DLestimate$estimate - DLestimate$SE * 1.96
DLestimate$upper <- DLestimate$estimate + DLestimate$SE * 1.96

DLestimate$lag <- 0:lag_max
p <- ggplot(DLestimate, aes(x=lag, y=estimate, ymin=lower, ymax=upper))
p <- p + geom_ribbon(alpha=.5) + geom_line(size=2)
p <- p + geom_line(aes(x=lag), linetype=2, size=2)
p <- p + theme_bw()
p

DLestimate<- data.frame(estimate=D%*%coef(fit)[dlparms])

cumulative <- sum(DLestimate$estimate)
cumulative

cumulative_se <- sqrt(sum(DLvar))
cumulative_se

cumulative_CI <- cumulative + cumulative_se * c(-1.96, 1.96)
cumulative_CI
